Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
init eval setup and add some charts for results

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}
\usepackage[ruled,vlined]{algorithm2e}
%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cleveref}

@@

In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
\begin{algorithm}
  \caption{Neighboring-Based Deep Q-Learning}
  \label{alg:neighbor_dqn}
  \ForEach{agent $i \in N$}{
      Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
      Initialize replay buffer $\mathcal{D}^i$
  }
  \For{episode = 1 to M}{
      \ForEach{agent $i \in N$}{
          Initialize initial observation $o_0^i$
      }
      \For{t = 0 to T}{
          \ForEach{agent $i \in N$}{
              Select action $a_t^i$ based on $\epsilon$-greedy policy using $Q^i(o_t^i, a^i; \theta^i)$\\
              Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{D}^i$\\
              Sample a mini-batch from $\mathcal{D}^i$\\
              Calculate target values using chosen neighboring strategy (see below)\\
              Update $\theta^i$ by minimizing the TD error\\
              Every C steps, update target network $\theta^{i-} \leftarrow \theta^i$\\
              \textbf{
              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
          }
      }
  }
\end{algorithm}

\section{Experimental Setup}\label{sec:experiments}
\begin{itemize}
\item Introduce the custom "collect the items" multi-agent environment:
\begin{itemize}
\item Describe the environment's dynamics, agent goals, and challenges.
\item Specify the action space (continuous and discrete) and observation space design.
\item Explain the reward structure, emphasizing the components that encourage cooperation.
\end{itemize}
\item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
\item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
\item Define the evaluation metrics: average episode length and average reward.
\end{itemize}

@@

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{graphicx}
\usepackage{autobreak}
\usepackage{mytodonotes}
\usepackage{subcaption}
\usepackage[ruled,vlined]{algorithm2e}
%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{cleveref}

@@

In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
\begin{algorithm}
  \caption{Neighboring-Based Deep Q-Learning}
  \label{alg:neighbor_dqn}
  \ForEach{agent $i \in N$}{
      Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
      Initialize replay buffer $\mathcal{D}^i$
  }
  \For{episode = 1 to M}{
      \ForEach{agent $i \in N$}{
          Initialize initial observation $o_0^i$
      }
      \For{t = 0 to T}{
          \ForEach{agent $i \in N$}{
              Select action $a_t^i$ based on $\epsilon$-greedy policy using $Q^i(o_t^i, a^i; \theta^i)$\\
              Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{D}^i$\\
              Sample a mini-batch from $\mathcal{D}^i$\\
              Calculate target values using chosen neighboring strategy (see below)\\
              Update $\theta^i$ by minimizing the TD error\\
              Every C steps, update target network $\theta^{i-} \leftarrow \theta^i$\\
              \textbf{
              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
          }
      }
  }
\end{algorithm}
\section{Experimental Setup}\label{sec:experiments}

To validate our approach, we developed a custom learning scenario using three State-of-the-Art frameworks 
  in Reinforcement Learning and Deep Learning, namely: \emph{Ray}~\cite{DBLP:conf/osdi/MoritzNWTLLEYPJ18} 
  (in particular, its module \emph{RLlib}~\cite{DBLP:conf/icml/LiangLNMFGGJS18}),
  \emph{Gymnasium}~\cite{DBLP:journals/corr/abs-2407-17032}
  and \emph{PyTorch}~\cite{DBLP:conf/nips/PaszkeGMLBCKLGA19}.

First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
  called \emph{collect the items} -- see \Cref{fig:env}.
%
This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
 are randomly placed.
%
The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
%
% Action space
%
% Obseration space

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/env.pdf}
  \caption{Graphical representation of the environment. 
  Specifically, the environment consists of a 2D euclidean space.
  The blue dots represent the agents, while the yellow stars represent the items that 
  the agents aim to collect.
  }
  \label{fig:env}
\end{figure}

% \begin{itemize}
% \item Introduce the custom "collect the items" multi-agent environment:
% \begin{itemize}
% \item Describe the environment's dynamics, agent goals, and challenges.
% \item Specify the action space (continuous and discrete) and observation space design.
% \item Explain the reward structure, emphasizing the components that encourage cooperation.
% \end{itemize}
% \item Detail the implementation framework (Gymnasium, RLlib, PyTorch).
% \item Specify the chosen RL algorithm (DQN) and its hyperparameter configuration.
% \item Define the evaluation metrics: average episode length and average reward.
% \end{itemize}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/episode_reward_mean.pdf}
  \includegraphics[width=1\linewidth]{figures/episode_len_mean.pdf}
  \caption{Training results...}
  \label{fig:results}
\end{figure}

\begin{figure*}[htb]
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{figures/mean-time-comparison-8-agents.pdf}
      %\caption{Start of the simulation.}
      % \label{fig:zones1}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{figures/mean-time-comparison-16-agents.pdf}
      %\caption{After k time steps of the simulation.}
      % \label{fig:zones2}
  \end{subfigure}
  \begin{subfigure}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{figures/mean-time-comparison-32-agents.pdf}
      %\caption{End of the simulation.}
      % \label{fig:zones3}
  \end{subfigure}
  \caption{ To-do
  }
  \label{fig:time-eval}
\end{figure*}
